Automated Verification for Real-Time Systems using Implicit Clocks and an Extended Antimirov Algorithm

### 2022-04-15 paper/tv.tex
m

void addNSugar (int n) 
/*req: true /\ _^*
  ens: d>=n /\ Sugar#d */
{ if (n == 0) { 
      event ["Sugar"];} 
  else {
      addOneSugar();
      addNSugar (n-1);}} 
\end{lstlisting}
\caption{Value-dependent specification.} 
\label{fig:Value_dependent_intro}
\vspace{0mm}
\end{wrapfigure}

@@

{
\begin{table*}[ht]
\centering
     % \vspace{0mm}
\caption{\label{tab:rewriting_tree_send} The inclusion proving example. }

@@

\item 
\textbf{Normalization.}
We present a set of normalization rules to soundly transfer the timed effects into a normal form, in particular after getting their derivatives. 
Before getting into the above inference rules, we assume that the effects formulae are tailored accordingly based on the axioms shown in
\tabref{table:normalization}
We built the axiom system on top of a complete axiom system \code{F_1}, from (A1) to (A10), suggested by \cite{DBLP:journals/jacm/Salomaa66}, 
which was designed for regular languages. We develop axioms (A11) 
to (A16) to further accommodate effects constructed by 
\code{||} and \code{\mysharp}.

\begin{table}[ht]
  \caption{Normalization Axioms for \timedEffects.}
  \label{table:normalization}
  \setlength{\tabcolsep}{10pt}
  \renewcommand{\arraystretch}{1.2}
  \centering
  \begin{tabular}{rl}
  \footnotesize

@@

\subsection{Implementation}
To show the feasibility of our approach, we have prototyped 
our automated verification system 
using OCaml. The proof obligations generated by the verifier 
are discharged using constraint solver Z3 
\citep{DBLP:conf/tacas/MouraB08}. 
We prove termination and soundness of the TRS. We validate 
the front-end forward verifier for conformance.

Based on these two benchmarks, we validate the verifier using 155  programs, varying from 15 lines to 300 lines. We manually annotate temporal specifications in our timed effects, including both succeeded and failed instances (roughly with the a 1:1 ratio). 
Out of the whole test suite, 101 were from the CEC benchmark, 54 were from the Hiphop.js benchmark.  Since async-await was inherited from JavaScript features, it only presents in the 54 hiphop.js programs.
We conduct experiments on a MacBook Pro with a 2.6 GHz Intel Core i7 processor. Given our benchmark, the running time varying from 0 to 500 ms.

@@

Meanwhile, we further demonstrate the flexibility and expressiveness of our effects logic.

@@

   %   \vspace{-2mm}
%(\code{\{Go\} \Rightarrow \_})
%(\code{\{Ready\} \Rightarrow \_}, \code{t_L^2 \Rightarrow true})
Termination of TRS is guaranteed because the set of derivatives to be considered is finite, and possible cycles are detected using \emph{memorization} \cite{DBLP:conf/tableaux/Brotherston05}, i.e., the rule \code{[REOCCUR]}. % Check out this following example:

@@

{
\begin{table}[ht]
      \vspace{0mm}
\caption{\label{tab:reoccur} The reoccurrence proving example. 
\code{I:} The main rewriting proof tree; \code{II:} Right hand side sub-tree of the rewriting process.}

@@

\code{I:}\
{

@@

\infer[dashed]1[{\textcircled{4}\siderule{[PROVE]}}]{
  \code{
    \textcolor {darkred}{True} : \epsilon \CONTAIN
    \textcolor {darkred}{True} : \epsilon
  }
}

\infer[dashed]1[{\textcircled{3}\siderule{[Normalisation]}}]{
  \code{
    \textcolor {darkred}{True} : \cancel{\{B\}} \CONTAIN
    \textcolor {darkred}{True} : \cancel{ \epsilon \cdot \{B\}}
  }
}

\infer[dashed]1[{\textcircled{2}\siderule{[UNFOLD]}}]{
  \code{
    \textcolor {darkred}{True} : \{B\} \CONTAIN
    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \mysharp  t_R \cdot \{B\}
  }
}
\hypo{\code{II}}

\infer[dashed]1[{\siderule{}}]{
  \code{
    \textcolor {darkred}{t_L{<}3} {:} \{A\}^\star \mysharp  t_L  \cdot  \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} {:} \{A\}^\star \mysharp  t_R  \cdot  \{B\}
  }
}

\infer[dashed]2[{\textcircled{1}\siderule{[Disj\text{-}L]}}]{
  \code{
    \textcolor {darkred}{t_L{<}3} : \{A\}^\star \mysharp  t_L \cdot \{B\}
    \vee \textcolor {darkred}{True} : \{B\} \CONTAIN
    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \mysharp  t_R \cdot \{B\}
  }
}
\end{prooftree}}
\\~\\

\hline \\
\code{II:} 
{\begin{prooftree}
\hypo{
  \code{
    \textcolor {
      darkred}{t_L^1{+}t_L^2{=}t_L \wedge t_L{<}3 \wedge t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
      \wedge t_L^2{=}t_R^2
    } \Rightarrow
    \textcolor {darkred}{t_R{<}4} 
%\qquad
%     \{A\}^\star \cdot \{B\}
%    \CONTAIN
%     \{A\}^\star \cdot \{B\}
  }
}

\infer[dashed]1[{\siderule{}}]{
  \code{
    \textcolor {
      darkred}{\cdots  \wedge  \cdots
%      
%      t_L^1{+}t_L^2{=}t_L{<}3  \wedge  t_R{=}t_R^1{+}t_R^2  \wedge  t_L^1{=}t_R^1
%       \wedge  t_L^2{=}t_R^2
    } :
     \{A\}^\star \mysharp  t_L^2 \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} :
     \{A\}^\star \mysharp  t_R^2 \cdot \{B\} \quad  \textcolor{darklavender}{(\ddagger)}
  }
}

\infer[dashed]1[{\textcircled{7}\siderule{[REOCCUR]}}]{
  \code{
    \textcolor {
      darkred}{
%t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2  \wedge       
       t_L^1{=}t_R^1
    } :
     \cancel{\{A\} \mysharp  t_L^1}  \cdot  \{A\}^\star \mysharp  t_L^2 \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} :
     \cancel{\{A\} \mysharp  t_R^1}  \cdot  \{A\}^\star \mysharp  t_R^2 \cdot \{B\}
  }
}

\infer[dashed]1[{\textcircled{6}\siderule{[UNFOLD]}}]{
  \code{
    \textcolor {darkred}{t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2} :
     ( \{A\} \mysharp  t_L^1  \cdot  \{A\}^\star \mysharp  t_L^2) \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} :
     ( \{A\} \mysharp  t_R^1  \cdot  \{A\}^\star \mysharp  t_R^2) \cdot \{B\}
  }
}

\infer[dashed]1[{\textcircled{5}\siderule{[SPLIT]}}]{
  \code{
    \textcolor {darkred}{t_L{<}3} : \{A\}^\star \mysharp  t_L \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} : \{A\}^\star \mysharp  t_R \cdot \{B\}  \quad \textcolor{darklavender}{(\ddagger)}
  }
}
\end{prooftree}}

@@

@@

  \begin{enumerate}
  \item \textbf{Axiom Rules:} 
  \input{rules/rule1}
  - It is easy to verify that antecedent of goal entailments in the rule \codeme{[Bot\text{-}LHS]} is unsatisfiable. Therefore, these entailments are evidently valid.\\
  - It is easy to verify that consequent of goal entailments in the rule \codeme{[Bot\text{-}RHS]} is unsatisfiable. Therefore, these entailments are evidently invalid.\\

  \item \textbf{Disprove Rules:} 
  \input{rules/rule2}
  - It's straightforward to prove soundness of the rule \codeme{[DISPROVE]}, Given that \codeme{ \es1} is nullable, while \codeme{ \es_2} is not nullable, thus clearly the antecedent contains more event traces than the consequent.  Therefore, these entailments are evidently invalid.\\

  \item \textbf{Prove Rules:} 
  \input{rules/rule3}
  - To prove soundness of the rule \code{[PROVE]}, we consider an arbitrary model, \codeme{d,  \varphi} such that:  \codeme{d,  \varphi \models  {\pi_1 : \es_1}}. Given the side conditions from the promises, we get \codeme{d,  \varphi \models {\pi_2 : \es_1}}. When the \code{\m{fst}} set of \code{\es_1} is empty, \code{\es_1} is possible \code{\bot} or \code{\epsilon}; and \code{\es_2} is nullable. For both cases, the inclusion is valid.

  - To prove soundness of the rule \codeme{[REOCCUR]}, we consider an arbitrary model, \codeme{d,  \varphi} such that:  \codeme{d,  \varphi \models  {\pi_1 : \es_1}}. Given the promises that  \codeme{\pi_1 : \es_1 \CONTAIN \pi_3 : \es_3}, we get \codeme{d,  \varphi \models {\pi_3 : \es_3}}; Given the promise that there exists a hypothesis \codeme{\pi_3 : \es_3 \CONTAIN  \pi_4 : \es_4}, we get \codeme{d,  \varphi \models {\pi_4 : \es_4}}; Given the promises that  \codeme{\pi_4 : \es_4 \CONTAIN \pi_2 : \es_2}, we get \codeme{d,  \varphi \models {\pi_2 : \es_2}}. Therefore,  the inclusion is valid. 
  \\

@@

  - To prove soundness of the rule \codeme{[UNFOLD]}, we consider an arbitrary model, \codeme{d_1,  \varphi_1} and \codeme{d_2,  \varphi_2}  such that:  \codeme{d_1,  \varphi_1 \models {\pi_1 : \es_1}} and \codeme{d_2,  \varphi_2 \models  {\pi_2 : \es_2}}. For an arbitrary event \codeme{(I, \pi, t)}, let \codeme{d_1^\prime, {\varphi_1}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket  \pi_1: \es_1 \rrbracket}; and 
  \codeme{d_2^\prime, {\varphi_2}^\prime \models \codeme{(I, \pi, t)}^{\text{-}1}\llbracket \pi_2 : \es_2 \rrbracket}.

  Case 1), \codeme{\codeme{(I, \pi, t)} \notin F}, \codeme{d_1^\prime, {\varphi_1}^\prime \models \bot }, thus automatically \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)};

  Case 2), \codeme{\codeme{(I, \pi, t)} \in F}, given that inclusions in the rule's premise is valid, then \codeme{d_1^\prime, {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)}.

  By \defref{Inclusion}, since for all \codeme{(I, \pi, t)}, \codeme{D^{\pi_1}_{\codeme{(I, \pi, t)}} (\es_1) \CONTAIN    D^{\pi_2}_{\codeme{(I, \pi, t)}}( \es_2)}, the conclusion is valid. 
  \\

>>>>

void addNSugar (int n) 
/*req: true/\ _^*
  ens: d>=n/\ Sugar#d */
{ if (n == 0) { 
      event ["Sugar"];} 
  else {
      addOneSugar();
      addNSugar (n-1);}} 
\end{lstlisting}
\caption{Value-dependent specification.} 
\label{fig:Value_dependent_intro}
\vspace{0mm}
\end{wrapfigure}

@@

{
\begin{table*}[ht]
\centering
     % \vspace{0mm}
\caption{\label{tab:rewriting_tree_send} The inclusion proving example. 
\code{I:} The main rewriting proof tree; \code{II:} Right hand side sub-tree of the rewriting process.}

@@

\item 
\textbf{Normalization.}
We present some normalization rules to soundly transfer the timed effects into a normal form, in particular after getting their derivatives. 
Before getting into the above inference rules, we assume that the effects formulae are tailored accordingly based on the axioms shown in
\tabref{table:normalization}
We built the axiom system on top of an axiom system \code{F_1}, from (A1) to (A10), suggested by \cite{DBLP:journals/jacm/Salomaa66}, 
which was designed for regular languages. We develop axioms (A11) 
to (A16) to further accommodate effects constructed by 
\code{||} and \code{\mysharp}.

\begin{table}[ht]
  \caption{Some Normalization Axioms for \timedEffects.}
  \label{table:normalization}
  \setlength{\tabcolsep}{10pt}
  \renewcommand{\arraystretch}{1.2}
  \centering
  \begin{tabular}{rl}
  \footnotesize

@@

To show the feasibility of our approach, we have prototyped 
our automated verification system 
using OCaml. The proof obligations generated by the verifier 
are discharged using constraint solver Z3 
\citep{DBLP:conf/tacas/MouraB08}. 
We prove termination and soundness of the TRS. We validate 
the front-end forward verifier against the state-of-the-art PAT 
\cite{DBLP:conf/cav/SunLDP09} model checker for conformance. 
Next, we show experimental results and case studies to evaluate the 
capability of our proposals.

\subsection{Experimental Results}
\label{subsec:Experimental_Results}

We conduct experiments on a MacBook Pro with a 2.6 GHz Intel Core i7 processor. Given our benchmark, the running time varying from 0 to 500 ms.

@@

%Meanwhile, we further demonstrate the flexibility and expressiveness of our effects logic.

@@

   %   \vspace{-2mm}
%(\code{\{Go\} \Rightarrow \_})
%(\code{\{Ready\} \Rightarrow \_}, \code{t_L^2 \Rightarrow true})
Termination of TRS is guaranteed because the set of derivatives 
to be considered is finite, and possible cycles are detected 
using \emph{memorization} \cite{DBLP:conf/tableaux/Brotherston05}, 
i.e., the rule $\codeme{[REOCCUR]}$. 
% Check out this following example:

@@

{
\begin{table}[ht]
      \vspace{0mm}
\caption{\label{tab:reoccur} The reoccurrence proving example. 
\code{(I)} The main rewriting proof tree; \code{(II)} Right hand side sub-tree of the rewriting process.}

@@

\code{(I):}\
{

@@

\infer[dashed]1[{\textcircled{4}\siderule{\codeme{[PROVE]}}}]{
  \code{
    \textcolor {darkred}{True} \wedge \epsilon \CONTAIN
    \textcolor {darkred}{True} \wedge \epsilon
  }
}

\infer[dashed]1[{\textcircled{3}\siderule{\codeme{[Normalisation]}}}]{
  \code{
    \textcolor {darkred}{True} \wedge \cancel{\{B\}} \CONTAIN
    \textcolor {darkred}{True} \wedge \cancel{ \epsilon \cdot \{B\}}
  }
}

\infer[dashed]1[{\textcircled{2}\siderule{\codeme{[UNFOLD]}}}]{
  \code{
    \textcolor {darkred}{True} \wedge \{B\} \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge \{A\}^\star \mysharp  t_R \cdot \{B\}
  }
}
\hypo{(\code{II})}

\infer[dashed]1[{\siderule{}}]{
  \code{
    \textcolor {darkred}{t_L{<}3}  \wedge  \{A\}^\star \mysharp  t_L  \cdot  \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4}  \wedge  \{A\}^\star \mysharp  t_R  \cdot  \{B\}
  }
}

\infer[dashed]2[{\textcircled{1}\siderule{\codeme{[OR\text{-}LHS]}}}]{
  \code{
    \textcolor {darkred}{t_L{<}3} \wedge \{A\}^\star \mysharp  t_L \cdot \{B\}
    \vee \textcolor {darkred}{True} \wedge \{B\} \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge \{A\}^\star \mysharp  t_R \cdot \{B\}
  }
}
\end{prooftree}}
\\~\\

\hline \\
\code{(II):} \qquad 
{\begin{prooftree}
\hypo{
  \code{
    \textcolor {
      darkred}{t_L^1{+}t_L^2{=}t_L \wedge t_L{<}3 \wedge t_R{=}t_R^1{+}t_R^2 \wedge t_L^1{=}t_R^1
      \wedge t_L^2{=}t_R^2
    } \Rightarrow
    \textcolor {darkred}{t_R{<}4} 
%\qquad
%     \{A\}^\star \cdot \{B\}
%    \CONTAIN
%     \{A\}^\star \cdot \{B\}
  }
}

\infer[dashed]1[{\siderule{}}]{
  \code{
    \textcolor {
      darkred}{\cdots  \wedge  \cdots
%      
%      t_L^1{+}t_L^2{=}t_L{<}3  \wedge  t_R{=}t_R^1{+}t_R^2  \wedge  t_L^1{=}t_R^1
%       \wedge  t_L^2{=}t_R^2
    } \wedge 
     \{A\}^\star \mysharp  t_L^2 \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge 
     \{A\}^\star \mysharp  t_R^2 \cdot \{B\} \quad  \textcolor{darklavender}{(\ddagger)}
  }
}

\infer[dashed]1[{\textcircled{7}\siderule{\codeme{[REOCCUR]}}}]{
  \code{
    \textcolor {
      darkred}{
%t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2  \wedge       
       t_L^1{=}t_R^1
    } \wedge 
     \cancel{\{A\} \mysharp  t_L^1}  \cdot  \{A\}^\star \mysharp  t_L^2 \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge 
     \cancel{\{A\} \mysharp  t_R^1}  \cdot  \{A\}^\star \mysharp  t_R^2 \cdot \{B\}
  }
}

\infer[dashed]1[{\textcircled{6}\siderule{\codeme{[UNFOLD]}}}]{
  \code{
    \textcolor {darkred}{t_L^1{+}t_L^2{=}t_L  \wedge  t_R{=}t_R^1{+}t_R^2} \wedge 
     ( \{A\} \mysharp  t_L^1  \cdot  \{A\}^\star \mysharp  t_L^2) \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge 
     ( \{A\} \mysharp  t_R^1  \cdot  \{A\}^\star \mysharp  t_R^2) \cdot \{B\}
  }
}

\infer[dashed]1[{\textcircled{5}\siderule{\codeme{[SPLIT]}}}]{
  \code{
    \textcolor {darkred}{t_L{<}3} \wedge \{A\}^\star \mysharp  t_L \cdot \{B\}
    \CONTAIN
    \textcolor {darkred}{t_R{<}4} \wedge \{A\}^\star \mysharp  t_R \cdot \{B\}  
    \quad \textcolor{darklavender}{(\ddagger)}
  }
}
\end{prooftree}}

@@

\subsection{Beyond Regular, Context-Free and Context-Sensitive}
%As explained in \secref{subsec:Specification_language}, t
The paradigmatic non-regular linear language: 
\code{t{>} 0 \wedge \anyevent{A}\mysharp{t}\cdot\anyevent{B}\mysharp{t}}, 
can be naturally expressed by the depended effects. 
Besides, the effects can also express grammars such as \code{t{>} 0 
\wedge \anyevent{A}\mysharp{t}\cdot\anyevent{B}\mysharp{t}
\cdot\anyevent{C}\mysharp{t}}, or 
\code{n{>} 0 \wedge m{>} 0 \wedge  \anyevent{A}\mysharp{n}
\cdot\anyevent{B}\mysharp{m}\cdot\anyevent{C}\mysharp{n}}, 
which are beyond context-free grammar.
%(by a contradiction proof using Pumping lemma) 
%and categorized as context-sensitive grammar. 
Those examples show that the traces which cannot be recognized 
even by push-down automata (PDA) can be represented by our effects. 
%As regular grammar and context-free grammar are equivalent to finite state automata (FSA) and  respectively, our effects can not be fully translated into either FSA or PDA.
However, such specifications are significant, suppose we 
have a traffic light control system, we could have a 
specifications \code{n{>} 0 \wedge m{>} 0 \wedge  
(\anyevent{Red}\mysharp{n}\cdot\anyevent{Yellow}\mysharp{m}\cdot
\anyevent{Green}\mysharp{n})^\star}, which specifies that  
(i) all the colors will occur at each life circle; and 
(ii) the duration of the green light and the red light is 
always the same. Moreover, these effects can not be translated 
into linear bounded automata (LBA) either, which equivalents to 
context-sensitive grammar, as LBA are only capable of expressing 
finite traces.

@@

  \begin{enumerate}
  \item \textbf{Axiom Rules:} 
  \input{rules/rule1}
  - It is easy to verify that antecedent of goal entailments in the rule $\codeme{[Bot\text{-}LHS]}$ is unsatisfiable. Therefore, these entailments are evidently valid.\\
  - It is easy to verify that consequent of goal entailments in the rule $\codeme{[Bot\text{-}RHS]}$ is unsatisfiable. Therefore, these entailments are evidently invalid.\\

  \item \textbf{Disprove Rules:} 
  \input{rules/rule2}
  - It's straightforward to prove soundness of the rule $\codeme{[DISPROVE]}$, Given that \codeme{\es1} is nullable, while \codeme{ \es_2} is not nullable, thus clearly the antecedent contains more event traces than the consequent.  Therefore, these entailments are evidently invalid.\\

  \item \textbf{Prove Rules:} 
  \input{rules/rule3}
  - To prove soundness of the rule $\codeme{[PROVE]}$, we consider an arbitrary model, \codeme{d, s, \varphi} such that:  
  \codeme{d,  s, \varphi \models  {\pi_1 \wedge \es_1}}. Given the side 
  conditions from the promises, we get \codeme{d,  s, \varphi \models 
  {\pi_2 \wedge \es_2}}. When the \code{\m{fst}} set of \code{\es_1} is 
  empty, \code{\es_1} is possible \code{\bot} or \code{\epsilon} and 
  \code{\pi_2 \wedge \es_2} is nullable. For both cases, the inclusion 
  is valid.

  - To prove soundness of the rule $\codeme{[REOCCUR]}$, we consider 
  an arbitrary model, \codeme{d, s, \varphi} such that:  \codeme{d,  s, 
  \varphi \models  {\pi_1 \wedge \es_1}}. Given the promises that  
  \codeme{\pi_1 \wedge \es_1 \CONTAIN \pi_3 \wedge \es_3}, we get 
  \codeme{d,  s, \varphi \models {\pi_3 \wedge \es_3}}; Given the 
  promise that there exists a hypothesis \codeme{\pi_3 \wedge \es_3 
  \CONTAIN  \pi_4 \wedge \es_4}, we get \codeme{d, s, \varphi \models 
  {\pi_4 \wedge \es_4}}; Given the promises that  
  \codeme{\pi_4 \wedge \es_4 \CONTAIN \pi_2 \wedge \es_2}, we get 
  \codeme{d, s,  \varphi \models {\pi_2 \wedge \es_2}}. Therefore,  
  the inclusion is valid. 
  \\

@@

  - To prove soundness of the rule $\codeme{[UNFOLD]}$, we consider an 
  arbitrary model, \codeme{d_1, s_1,  \varphi_1} and \codeme{d_2, s_2,
   \varphi_2}  such that:  \codeme{d_1, s_1,  \varphi_1 \models {\pi_1 \wedge
    \es_1}} and \codeme{d_2, s_2,  \varphi_2 \models  {\pi_2 \wedge \es_2}}. 
    For an arbitrary event \codeme{h}, let \codeme{d_1^\prime, s_1^\prime,
     {\varphi_1}^\prime \models \codeme{h}^{\text{-}1}\llbracket  \pi_1\wedge \es_1 \rrbracket}; 
     and 
  \codeme{d_2^\prime, s_2^\prime, {\varphi_2}^\prime \models 
  \codeme{h}^{\text{-}1}\llbracket \pi_2 \wedge \es_2 \rrbracket}.

  Case 1), \codeme{\codeme{h} \notin F}, 
  \codeme{d_1^\prime, {\varphi_1}^\prime \models \bot }, 
  thus automatically \codeme{d_1^\prime, {\varphi_1}^\prime 
  \models D^{\pi_2}_{\codeme{h}}( \es_2)};

  Case 2), \codeme{\codeme{h} \in F}, given that inclusions 
  in the rule's premise is valid, then \codeme{d_1^\prime, s_1^\prime, 
  {\varphi_1}^\prime \models D^{\pi_2}_{\codeme{h}}( \es_2)}.

  By \defref{Inclusion}, since for all \codeme{h}, 
  \codeme{D^{\pi_1}_{\codeme{h}} (\es_1) \CONTAIN   
   D^{\pi_2}_{\codeme{h}}( \es_2)}, the conclusion is valid. 
  \\
